Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer

### 2020-07-29 main.tex
:art: IRS optimization

		Similar to \cite{Huang2017}, we further stack up channel and waveform vectors over all subbands to define $\boldsymbol{h}=[\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$. Moreover, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries. On top of this, $z$ is reduced to \ref{eq:z_expand} with DC terms expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\label{eq:z_expand}\\
				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
				& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\label{eq:y_I2}\\
				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
				& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\\
				\mathcal{A}\left\{y_{P}^2(t)\right\}
				& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\\
				\mathcal{A}\left\{y_{P}^4(t)\right\}
				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\label{eq:y_P4}
				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\\
				& = \frac{1}{2}\beta_2\rho(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h})\nonumber\\
				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\right)\nonumber\\
				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h})\label{eq:z_expand_1}\\
				& = \frac{1}{2}\beta_2\rho(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\nonumber\\
				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}\boldsymbol{w}_P)^H \right)\nonumber\\
				& \quad+ \frac{3}{2}\beta_4\rho^2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,0}\boldsymbol{w}_P)\label{eq:z_expand_2}
	\end{subsection}

@@

\begin{section}{Problem Formulation}
	We characterize the R-E region through multiple current maximization problems subject to transmit power, IRS magnitude, and different rate constraints
	\begin{maxi!}
		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{\label{eq:su_target}}
		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
		\addConstraint{R \ge \bar{R}}\label{eq:su_rate_constraint}
		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
		\addConstraint{0 \le \rho \le 1}
	\end{maxi!}
	Problem \ref{op:su} is intricate with coupled variables involved in non-convex objective function \ref{eq:su_target} and rate constraint \ref{eq:su_rate_constraint}. To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform together with receive splitting ratio until convergence.

	\begin{subsection}{IRS Phase Shift}
		We optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{I/P,n}$ and splitting ratio $\rho$. Since
		\begin{equation}\label{eq:h_n_outer_product}
				\boldsymbol{h}_n\boldsymbol{h}_n^H
				&=(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\\
				&=\boldsymbol{h}_{D,n}\boldsymbol{h}_{D,n}^H+\boldsymbol{V}_n^H\boldsymbol{\phi}\boldsymbol{h}_{D,n}^H+\boldsymbol{h}_{D,n}\boldsymbol{\phi}^H\boldsymbol{V}_n+\boldsymbol{V}_n^H\boldsymbol{\phi}\boldsymbol{\phi}^H\boldsymbol{V}_n\\
				&=\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n
		where $t$ is an auxiliary variable with unit modulus and
		\begin{equation}\label{eq:M_n,phi}
			\boldsymbol{M}_n=
			\begin{bmatrix}
				\boldsymbol{V}_n \\
				\boldsymbol{h}_{D,n}^H
			\end{bmatrix} \in \mathbb{C}^{(L+1) \times M},
			\quad \bar{\boldsymbol{\phi}}=\
			\begin{bmatrix}
				\boldsymbol{\phi} \\
				t
			\end{bmatrix},
			\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
		Therefore, it holds that
				\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2
				&=\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\\
				&=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\\
				&=\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
		with
		\begin{equation}\label{eq:C_n}
			\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}
		Similarly, we have
			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}
		where
		\begin{equation}\label{eq:M}
			\boldsymbol{M}=
			\begin{bmatrix}
				\boldsymbol{V} \\
				\boldsymbol{h}_D^H
			\end{bmatrix} \in \mathbb{C}^{(L+1) \times MN}
		Next, introduce auxiliary variables
		\begin{equation}\label{eq:t}
				t_{I/P,n}
				&=\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*\boldsymbol{h}\\
				&=\mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n}^*)\\
				&=\mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*)\\
				&=\mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H\boldsymbol{\Phi})\\
				&=\mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
		with
		\begin{equation}\label{eq:C_{I/P,n}}
			\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}
		Therefore, \ref{eq:z_channel} rewrites as
		\begin{equation}\label{eq:z_irs}
				z(\boldsymbol{\Phi})
				&=\frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\\
				&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\\
				&\quad+\frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}
		We use first-order Taylor expansion to approximate the second-order terms in \ref{eq:z_irs}. Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}
			(t_{I,0}^{(i)})^2
			& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\label{eq:t_{I,0}_square}\\
			t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
			& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\\
			t_{I,0}^{(i)} t_{P,0}^{(i)}
			& = \frac{1}{4}(t_{I,0}^{(i)} + t_{P,0}^{(i)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\nonumber\\
			& \ge \frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})\nonumber\\
			& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_{I/P,0}}
		\ref{eq:t_{I,0}_square} -- \ref{eq:t_{I/P,0}} provide lower bounds to the corresponding terms in \ref{eq:z_irs}, and the approximated current function at iteration $i$ is given in \ref{eq:z_irs_approx}.
			\begin{equation}\label{eq:z_irs_approx}
					\tilde{z}(\boldsymbol{\Phi}^{(i)})
					& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}^{(i)}+t_{P,0}^{(i)})\\
					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1}{2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*}\right)\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)}) - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\right)
		Hence, problem \ref{op:su} is transformed to
			{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
			\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
			\addConstraint{\boldsymbol{\Phi}\succeq{0}}
			\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
		We then relax the rank constraint \ref{co:irs_rank} and solve the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ iteratively by interior-point method. If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD). Otherwise, a solution can be extracted through Gaussian randomization method \cite{Huang2010}. We first perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$. Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates by
			\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}
		The candidate maximizing the objective function \ref{eq:su_irs_target} is chosen as the optimal solution $\bar{\boldsymbol{\phi}}^\star$. Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:ff_irs}.
			\caption{IRS Phase Shift}
			\label{al:ff_irs}
				\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_D,\boldsymbol{h}_I,\boldsymbol{h}_R,Q,\bar{R},\epsilon,\rho,\boldsymbol{w}_{I/P},\sigma_n \ \forall n$
				\State \textbf{Initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}
				\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:M}, \ref{eq:M_n,phi}, \ref{eq:C_n}, \ref{eq:C_{I/P,n}}
				\Repeat;
				\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs}
				\State Update auxiliary $t_{I/P,n}^{(i)} \forall n$ by \ref{eq:t} for SCA

>>>>

		Similar to \cite{Huang2017}, we further stack up channel and waveform vectors over all subbands to define $\boldsymbol{h}=[\boldsymbol{h}_1^H,\dots,\boldsymbol{h}_N^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^H,\dots,\boldsymbol{w}_{I/P,N}^H]^H \in \mathbb{C}^{MN \times 1}$. Moreover, let $\boldsymbol{W}_{I/P,n}$ keep the $n$-th ($n=-N+1,\dots,N-1$) block diagonal of $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$ and null the remaining entries. On top of this, $z$ is reduced to \ref{eq:z_expand} with DC terms expressed in \ref{eq:y_I2} -- \ref{eq:y_P4}.
		\begin{figure*}[b]
			\hrule
			\begin{align}
				z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)
				& = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P}^2(t)\right\}\Bigr)\label{eq:z_expand}\\
				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^2(t)\right\}\right\}
				& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h}\label{eq:y_I2}\\
				\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}
				& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{I,0}\boldsymbol{h})^2\\
				\mathcal{A}\left\{y_{P}^2(t)\right\}
				& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{P,n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{P,0}\boldsymbol{h}\\
				\mathcal{A}\left\{y_{P}^4(t)\right\}
				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{P,{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{P,{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{P,{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{P,{n_4}})^H} = \frac{3}{8}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{P,n}\boldsymbol{h})^H\label{eq:y_P4}
			\end{align}
		\end{figure*}
	\end{subsection}

@@

\begin{section}{Problem Formulation}
	We characterize the R-E region through multiple current maximization problems subject to transmit power, IRS magnitude, and different rate constraints
	\begin{maxi!}
		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:original}}{\label{eq:su_target}}
		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
		\addConstraint{R \ge \bar{R}}\label{eq:su_rate_constraint}
		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
		\addConstraint{0 \le \rho \le 1}
	\end{maxi!}
	Problem \ref{op:original} is intricate with coupled variables involved in non-convex objective function \ref{eq:su_target} and rate constraint \ref{eq:su_rate_constraint}. To reduce the design complexity, we propose an suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform together with receive splitting ratio until convergence.

	\begin{subsection}{IRS Phase Shift}
		In this section, the IRS phase shift $\boldsymbol{\phi}$ is optimized for any given waveform $\boldsymbol{w}_{I/P}$ and splitting ratio $\rho$. We observe that
		\begin{equation}
			\begin{split}
				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2
				& = \boldsymbol{w}_{I,n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}\\
				& = \boldsymbol{w}_{I,n}^H(\boldsymbol{h}_{D,n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\\
				& = \boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{I,n}\\
				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\\
				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
			\end{split}
		\end{equation}
		where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{D,n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Similarly, we define $t_{I/P,n}$ ($n=-N+1,\dots,N-1$) as
		\begin{equation}
			\begin{split}
				t_{I/P,n}
				& = \boldsymbol{h}^H\boldsymbol{W}_{I/P,n}\boldsymbol{h}\\
				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{I/P,n})\\
				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{I/P,n}\right)\\
				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n})\\
				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H\boldsymbol{\Phi})\\
				& = \mathrm{Tr}(\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi})
			\end{split}
		\end{equation}
		where $\boldsymbol{h}_D=[\boldsymbol{h}_{D,1}^H,\dots,\boldsymbol{h}_{D,N}^H]^H \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.

		Therefore, the objective function \ref{eq:z_expand} rewrites as
		\begin{equation}\label{eq:z_irs}
			\begin{split}
				z(\boldsymbol{\Phi})
				&=\frac{1}{2}{\beta_2}{\rho}(t_{I,0}+t_{P,0})\\
				&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\\
				&\quad+\frac{3}{2}{\beta_4}{\rho^2}t_{I,0}t_{P,0}
			\end{split}
		\end{equation}

		To maximize non-concave expression \ref{eq:z_irs}, we use first-order Taylor expansion to approximate its second-order terms. Based on the variables optimized at iteration $i - 1$, the local approximation at iteration $i$ suggests \cite{Adali2010}
		\begin{align}
			(t_{I,0}^{(i)})^2
			& \ge 2 t_{I,0}^{(i)}t_{I,0}^{(i-1)} - (t_{I,0}^{(i-1)})^2\label{eq:t_{I,0}_square}\\
			t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
			& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\\
			t_{I,0}^{(i)} t_{P,0}^{(i)}
			& = \frac{1}{4}(t_{I,0}^{(i)} + t_{P,0}^{(i)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\nonumber\\
			& \ge \frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})\nonumber\\
			& \quad - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\label{eq:t_{I/P,0}}
		\end{align}
		which provide lower bounds to the corresponding terms in \ref{eq:z_irs}. At iteration $i$, the approximated objection function $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ is detailed in \ref{eq:z_irs_approx}.
		\begin{figure*}[b]
			\hrule
			\begin{equation}\label{eq:z_irs_approx}
				\begin{split}
					\tilde{z}(\boldsymbol{\Phi}^{(i)})
					& = \frac{1}{2}{\beta_2}{\rho}(t_{I,0}^{(i)}+t_{P,0}^{(i)})\\
					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - 2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1}{2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*}\right)\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{I,0}^{(i)} + t_{P,0}^{(i)})(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)}) - \frac{1}{4}(t_{I,0}^{(i-1)} + t_{P,0}^{(i-1)})^2 - \frac{1}{4}(t_{I,0}^{(i)} - t_{P,0}^{(i)})^2\right)
				\end{split}
			\end{equation}
		\end{figure*}
		Hence, problem \ref{op:original} is transformed to
		\begin{maxi!}
			{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{eq:su_irs_target}}
			\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}\label{co:irs_rate}
			\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
			\addConstraint{\boldsymbol{\Phi}\succeq{0}}
			\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
		\end{maxi!}

		Problem \ref{op:irs} is not a standard Semi-Definite Programming (SDP) due to the rate constraint \ref{co:irs_rate}. Therefore, even if we relax the rank constraint \ref{co:irs_rank} to formulate a convex problem, there is no guarantee that the optimal rank-1 solution $\bar{\boldsymbol{\phi}}^{\star}$ extracted from $\boldsymbol{\Phi}^{\star}$ is a stationary point of the original problem \ref{op:original}. In Section [TODO], we numerically show that $\boldsymbol{\Phi}^{\star}$ is rank-1 for all tested channel realizations so that the performance loss is insignificant.
